Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-16 manuscript/draft.Rmd

>>>>

[[Note: this paragraph may no longer be accurate!]] For the error metric that
evaluates both models' point estimates and their uncertainty simultaneously, the
JSDM and the nonlinear richness model converge towards the time-series baselines
at the longest time-scales assessed. This convergence at longer time scales
highlights the importance of considering how forecasting method performance
changes with the distance into the future being predicted (Box 1). The value of
this approach, and associated forecast horizons, has been raised for knowing how
far into the future a model can be effectively used for forecasting
[@petchey2015], but our results suggest a broader value to this approach for
considering the potential importance of different models and processes for
making forecasts at different scales. Our results show that for forecasts 1-3
years in the future, baselines and time-series based approaches outperform all
other methods using integrative metrics. At these time scales, environmental
changes are relatively small and changes in the biota may lag behind changes in
the environment. However, as the timescale of the forecast increases to a decade
the JSDMs and environmental richness models get closer to the accuracy of the
time-series methods and even surpass some of those methods. As the forecast
distance increases the amount of environmental change is expected to increase
and the system will have more time to respond, potentially leading to shifts
towards improved relative performance of the models incorporating environmental
and ecological information. If this shift with forecast distance in the relative
importance of different processes and models continues, this could lead to JSDMs
and environmental richness models outperforming time-series based approaches at
sufficiently long time scales. These results suggest that assessment of how
forecast performance changes with time lag is not only important for determining
how far in the future to forecast, but also for determining which models and
processes are most relevant for making forecasts at different time scales. For
example ensemble forecasts could be created which incorporate these time lags
into the weights for individual models.
